Additional analysis

### 2020-01-21 analysis/03_additional-analysis.Rmd
Add original interacted regressions + probit for likelihood collapse

```{r load-libraries-data, warning=FALSE, message=FALSE}
# Load libraries
library(tidyverse)
library(crackdownsphilanthropy)
library(magrittr)
library(rstan)
library(broom)
library(glue)
library(grid)
library(gridExtra)
library(Gmisc)
library(pander)
library(scales)
library(ipumsr)
library(here)

@@

@@

@@

>>>>

```{r load-libraries-data, warning=FALSE, message=FALSE}
# Load libraries
library(tidyverse)
library(crackdownsphilanthropy)
library(magrittr)
library(rstan)
library(rstanarm)
library(broom)
library(glue)
library(grid)
library(gridExtra)
library(Gmisc)
library(pander)
library(scales)
library(ipumsr)
library(huxtable)
library(here)

@@

# Print correct huxtable table depending on the type of output.
#
# Technically this isn't completely necessary, since huxtable can output a
# markdown table, which is ostensibly universal for all output types. However,
# markdown tables are inherently limited in how fancy they can be (e.g. they
# don't support column spans), so I instead let the regression table use
# huxtable's fancy formatting for html and PDF and markdown everywhere else.
if (isTRUE(getOption('knitr.in.progress'))) {
  file_format <- rmarkdown::all_output_formats(knitr::current_input())
} else {
  file_format <- ""
}

print_hux <- function(x) {
  if ("html_document" %in% file_format) {
    print_html(x)
  } else if ("pdf_document" %in% file_format) {
    print_latex(x)
  } else if ("word_document" %in% file_format) {
    print_md(x)
  } else {
    print(x)
  }
}

@@

# Balance

```{r}

```

@@

# Results using interaction terms

In our preregistration protocol, we said we'd calculate the differences in group means using a regression model with 3-way interaction terms. This was mostly for the sake of simplicity—running one model is easier than running multiple individual tests—but the interpretation is a complicated mess. So instead, we ran individual difference in mean tests for the actual paper. For the sake of transparency, though, here are the results from the fully interacted regression models.

## Interpreting interactions in models

Ordinarily, people use ANOVA to analyze 3-way, 2 × 2 × 2 factorial designs, [like this](https://mypages.valdosta.edu/mwhatley/3600/2x2x2.htm). A more flexible ([yet identical!](https://www.theanalysisfactor.com/why-anova-and-linear-regression-are-the-same-analysis/)) way to do this is to use a regular regression model with interaction terms for each of the conditions, like so (here we use three, since we can use simper models to get averages for the larger umbrella groups, like just crackdowns and crackdown + issue):

- Model 1:

    $$
    y = \beta_0 + \beta_1 \text{Crackdown}
    $$

- Model 2:

    $$
    \begin{aligned}
    y =& \beta_0 + \beta_1 \text{Crackdown} + \beta_2 \text{Issue } + \\
    & \beta_3 \text{Crackdown} \times \text{Issue}
    \end{aligned}
    $$

- Model 3:

    $$
    \begin{aligned}
    y =& \beta_0 + \beta_1 \text{Crackdown} + \beta_2 \text{Issue} + \beta_3 \text{Funding } + \\
    & \beta_4 \text{Crackdown} \times \text{Issue } + \\
    & \beta_5 \text{Crackdown} \times \text{Funding } + \\
    & \beta_6 \text{Issue} \times \text{Funding } + \\
    & \beta_7 \text{Crackdown} \times \text{Issue} \times \text{Funding}
    \end{aligned}
    $$

Adding different combinations of the coefficients provides the average values for each combination of factors, which corresponds to the average likelihood and amount donated.

```{r interaction-interpretation, warning=FALSE, message=FALSE, results="asis"}
model1 <- "1"
model2 <- "2"
model3 <- "3"

interpretation <- tribble(
  ~Model, ~`Coefficients to add together`,
  model3, "Intercept",
  model3, "Intercept + Funding",
  model2, "Intercept",
  model3, "Intercept + Issue",
  model3, "Intercept + Issue + Funding + (Issue × Funding)",
  model2, "Intercept + Issue",
  model1, "Intercept",
  model3, "Intercept + Crackdown",
  model3, "Intercept + Crackdown + Funding + (Crackdown × Funding)",
  model2, "Intercept + Crackdown",
  model3, "Intercept + Crackdown + Issue + (Crackdown × Issue)",
  model3, "Intercept + Crackdown + Issue + Funding + (Crackdown × Issue) + (Crackdown × Funding) + (Issue × Funding) + (Crackdown × Issue × Funding)",
  model2, "Intercept + Crackdown + Issue + (Crackdown × Issue)",
  model1, "Intercept + Crackdown"
)

conditions_summary <- bind_rows(group_by(results, crackdown, issue, funding) %>% nest(),
                                group_by(results, crackdown, issue) %>% nest(),
                                group_by(results, crackdown) %>% nest(),
                                results %>% nest(data = everything())) %>% 
  arrange(crackdown, issue, funding) %>% 
  select(-data) %>% ungroup() %>% 
  mutate(funding = ifelse(is.na(funding) & !is.na(issue) , "*Total*", as.character(funding)),
         issue = ifelse(is.na(issue) & !is.na(crackdown), "*Total*", as.character(issue)),
         crackdown = ifelse(is.na(crackdown), "*Total*", as.character(crackdown))) %>% 
  group_by(crackdown) %>% 
  mutate(issue = replace(issue, duplicated(issue), NA)) %>% 
  ungroup() %>% 
  mutate(crackdown = replace(crackdown, duplicated(crackdown), NA)) %>% 
  rename(`Crackdown condition` = crackdown, `Issue condition` = issue,
         `Funding condition` = funding)

conditions_summary %>% 
  slice(-n()) %>% 
  bind_cols(interpretation) %>% 
  pandoc.table()
```

## Amount donated

```{r build-models-amount, warning=FALSE, message=FALSE, results="hide", cache=TRUE}
# Basic interaction models
m_amount_c <- stan_glm(amount_donate ~ crackdown,
                       data = results, family = gaussian(),
                       prior = cauchy(location = 0, scale = 2.5),
                       prior_intercept = cauchy(location = 0, scale = 10),
                       chains = CHAINS, iter = ITER, warmup = WARMUP, seed = BAYES_SEED)

m_amount_ci <- update(m_amount_c, . ~ . + issue + crackdown * issue)
m_amount_cif <- update(m_amount_c, . ~ . + 
                         issue + funding + crackdown * issue + crackdown * funding + 
                         issue * funding + crackdown * issue * funding)
# Models with just issue and just funding
m_amount_i <- update(m_amount_c, . ~ issue)
m_amount_f <- update(m_amount_c, . ~ funding)
```

```{r tbl-models-amount, warning=FALSE, results="asis"}
# Get subset of coefficients
coefs_to_include <- list(m_amount_c, m_amount_ci, m_amount_cif) %>% 
  map(~ tidy(.)) %>% bind_rows() %>% distinct(term) %>% pull(term)

huxreg(m_amount_c, m_amount_ci, m_amount_cif, 
       coefs = coefs_to_include,
       statistics = c(Observations = "nobs",
                       `Posterior sample size` = "pss",
                       Sigma = "sigma"),
       stars = NULL) %T>% 
  print_hux() %>% 
  to_md(max_width = 100) %>% 
  cat(file = here("analysis", "output", "tables", "tbl-interactions-amount.md"))
```

## Likelihood of donation

```{r build-models-likely, warning=FALSE, message=FALSE, reuslts="hide", cache=TRUE}
# Basic interaction models
# Weakly informative student t priors, since these coefficients are log-odds
# See https://github.com/stan-dev/stan/wiki/Prior-Choice-Recommendations#prior-for-the-regression-coefficients-in-logistic-regression-non-sparse-case and https://arxiv.org/abs/1507.07170
m_likely_c <- stan_glm(donate_likely_bin ~ crackdown,
                       data = results, family = binomial(link = "logit"),
                       prior = student_t(3, 0, 2.5),
                       prior_intercept = student_t(3, 0, 10),
                       chains = CHAINS, iter = ITER, warmup = WARMUP, seed = BAYES_SEED)

m_likely_ci <- update(m_likely_c, . ~ . + issue + crackdown * issue)

m_likely_cif <- update(m_likely_c, . ~ . + 
                         issue + funding + crackdown * issue + crackdown * funding + 
                         issue * funding + crackdown * issue * funding)

# Models with just issue and just funding
m_likely_i <- update(m_likely_c, . ~ issue)
m_likely_f <- update(m_likely_c, . ~ funding)
```

```{r tbl-models-likely, warning=FALSE, results="asis"}
# Get subset of coefficients
coefs_to_include <- list(m_likely_c, m_likely_ci, m_likely_cif) %>% 
  map(~ tidy(.)) %>% bind_rows() %>% distinct(term) %>% pull(term)

huxreg(m_likely_c, m_likely_ci, m_likely_cif, 
       coefs = coefs_to_include,
       statistics = c(Observations = "nobs",
                       `Posterior sample size` = "pss",
                       Sigma = "sigma"),
       stars = NULL) %T>% 
  print_hux() %>% 
  to_md(max_width = 100) %>% 
  cat(file = here("analysis", "output", "tables", "tbl-interactions-likelihood.md"))
```

# Collapsing likelihood variable

To simplify our analysis, we collapse our likelihood scale from a 1-5 Likert scale to a binary variable:

```{r show-collapsed-levels, results="asis"}
collapsed_likelihood <- tribble(
  ~`Original answer`, ~`Collapsed answer`,
  "Extremely likely", "Likely",
  "Somewhat likely", "Likely",
  "Neither likely nor unlikely", "Unlikely",
  "Somewhat unlikely", "Unlikely",
  "Extremely unlikely", "Unlikely"
)

collapsed_likelihood %>% 
  pandoc.table(justify = "ll")
```

To check that the results are internally consistent when collapsed, we ran an ordered probit model 
(using Stan) to see if the cutpoints follow the distribution of answers, and they do. "Somewhat likely" and above has a cutpoint of > 0.18, meaning that the likelihood is positive on average for both "Somewhat likely" and "Extremely likely."

```{r collapsed-probit, warning=FALSE, message=FALSE, results="hide", cache=TRUE}
collapsed_oprobit <- stan_polr(donate_likely ~ crackdown, data = results,
                               prior = R2(0.25, what = "mean"), prior_counts = dirichlet(1),
                               method = "probit")
```

```{r show-collapsed-probit, results="asis"}
huxreg(collapsed_oprobit,
       coefs = c("Crackdown" = "crackdownCrackdown",
                 "Cutpoint: Extremely unlikely|Somewhat unlikely" = 
                   "Extremely unlikely|Somewhat unlikely",
                 "Cutpoint: Somewhat unlikely|Neither likely nor unlikely" = 
                   "Somewhat unlikely|Neither likely nor unlikely",
                 "Cutpoint: Neither likely nor unlikely|Somewhat likely" = 
                   "Neither likely nor unlikely|Somewhat likely",
                 "Cutpoint: Somewhat likely|Extremely likely" = 
                   "Somewhat likely|Extremely likely"),
       statistics = c(Observations = "nobs",
                       `Posterior sample size` = "pss"),
       stars = NULL) %>%
  set_align(everywhere, 1, "left") %>% 
  set_align(everywhere, 2, "center") %>% 
  set_position("left") %>% 
  set_caption("Ordered probit regression with donation likelihood as outcome variable {#tbl:probit-likelihood}") %T>% 
  print_hux() %>% 
  to_md(max_width = 140) %>% 
  cat(file = here("analysis", "output", "tables", "tbl-probit-likelihood.md"))
```
